---
name: Jason M. Bryer, Ph.D.
surname: 
position: "Assistant Professor"
# address: "Albany, NY"
# phone: 518-464-8594
www: www.bryer.org
email: "jason@bryer.org"
twitter: jbryer
github: jbryer
linkedin: jasonbryer
# aboutme: 
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141 # use black color
output:
  vitae::moderncv:
    theme: classic
    keep_tex: no
    keep_md: no
    pandoc_args: ["--lua-filter=lua/multiple-bibliographies.lua"]
bibliography_published: "bib/Published.bib"
bibliography_presentations: "bib/Presentations.bib"
bibliography_inprep: "bib/Working.bib"
bibliography_software: "bib/Software.bib"
csl: "apa7-cv.csl"
nocite: "@*"
editor_options: 
  chunk_output_type: console
---


```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(readxl)
library(tibble)
library(tidyverse)

```

# Professional Interests

Teaching and research within K-12, higher education, and data science. Specific areas of interest include reproducible research; self-regulated learning; formative assessment; issues of social justice and equity in education; and statistics and methodology with an emphasis on propensity score analysis and modern graphics.

# Education

```{r education}
education <- readxl::read_excel('data/Education.xlsx')
education %>% detailed_entries(Degree, Year, Institution, Where)
```

# Dissertation

```{r dissertation}
tribble(
  ~ Description, ~ Label, ~ Other,
  "A National Study Comparing Charter and Traditional Public Schools Using Propensity Score Analysis", "Title", "",
  "Robert M. Pruzek (chair), Bruce Dudek (co-chair), Heidi Andrade, Kathryn S. Schiller", "Committee", "",
  "https://github.com/jbryer/Dissertation", "Website", ""
) %>% 
  brief_entries(Description, Label, Other)

```

# Professional Experiences

```{r experiences}
experiences <- readxl::read_excel('data/Experience.xlsx')
experiences %>% detailed_entries(
  what = Title, 
  when = paste0(Start, ' - ', End), 
  with = Institution,
  where = Location,
  why = Description
  )
```

# Teaching Experiences

```{r teaching}
teaching <- readxl::read_excel('data/Teaching.xlsx')
teaching %>% detailed_entries(
  what = Title, 
  when = Date, 
  # with = Institution,
  where = Location,
  why = Description
  )
```

# Service Positions

\cvline{2014-present}{Founding Organizer of the Albany R Users Group\newline Website: \url{http://www.meetup.com/Albany-R-Users-Group}}

\subsection{\textbf{Dissertation Committees}}
\cvline{current}{David Franklin - Relationship between grit, mindset, and academic achievement}
\cvline{2020}{Jana L. Vanderslice-Barr - Demographic Differences in Post-Secondary Outcomes Following Participation in the Diagnostic Assessment and Achievement of College Skills Intervention}
\cvline{2019}{Erica Pawlo - Identifying Profiles of Motivational Processes in Online College Students and Their Relations to Multiple Indicators of Academic Success}
\cvline{2018}{Kimberly Speershneider - The Differentiated Impact Of Early Entry Into Head Start On Social Competence And Literacy: An Applied Propensity Score Analysis}
\cvline{2015}{Chrisopher Valle - Effects Of Criteria-Referenced Formative Assessment On Achievement In Music}
\cvline{2015}{Fei Chen - The Impact of Criteria-Referenced Formative Assessment On Fifth Grade Students' Theater Arts
And English Language Arts Achievement}

\subsection{\textbf{Excelsior College}}
\cvline{2019-2020}{Committee Member, Course Evaluation Committee}

\subsection{\textbf{Excelsior College}}
\cvline{2015-2019}{Chair, Diagnostic Assessment \& Achievement of College Skills Advisory Committee}
\cvline{2014-2018}{Chair, Technology Advisory Committee}
\cvline{2014-2018}{Committee Member, Information Technology Council}
\cvline{2017-2018}{Committee Member, Academic Affairs Council}
\cvline{2013-2014}{Committee Member, Persistence Measure Task Force}
\cvline{2010-2014}{Committee Member, Student Learning Support Services Committee}
\cvline{2010-2014}{Committee Member, Data Definitions \& Quality}
\cvline{2010-2013}{Committee Member, Information Technology Operations \& Security Committee}
\cvline{2011-2012}{Committee Member, Search Committee for Assistant Provost}
\cvline{2009-2010}{Committee Member, Early Alert System for Identifying Non-Persistent Students}
\cvline{2009}{Chair, Task Force on a Library of Model Courses}
\cvline{2009-2010}{Committee Member, System for Storing Information at Excelsior College}

\subsection{\textbf{City School District of Albany}}
\cvline{2011-2012}{\small Committee Member, Grade Configuration Committee; Chair of the Accountability Subcommittee}

\subsection{\textbf{American Educational Research Association}}
\cvline{2009-2011}{Treasurer, Studying and Self-Regulated Learning Special Interest Group}
\cvline{2009-2010}{Committee Member, Division D Membership Committee}

\subsection{\textbf{University at Albany, Division of Educational Psychology \& Methodology}}
\cvline{2007-2008}{Treasurer, Graduate Student Organization}


# Professional Memberships

\cvline{AERA}{\href{http://aera.net}{American Educational Research Association}}
\cvline{ASA}{\href{http://www.amstat.org/}{American Statistical Association}}
\cvline{NCME}{\href{http://www.ncme.org}{National Council on Measurement in Education}}
\cvline{NEAIR}{\href{http://www.neair.org}{North East Association for Institutional Research}}


# Awards \& Grants

```{r awards}
awards <- readxl::read_excel('data/Awards.xlsx')
awards %>% 
	mutate(Title = replace_na(Title, '')) %>%
	brief_entries(
		paste0(Title, ' ', Description, na.print=''), 
		Year )
```



# Publications

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_published}
:::

\endgroup


# Working Papers

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_inprep}
:::


\endgroup


# Presentations

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_presentations}
:::

\endgroup



# Software

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

::: {#refs_software}
:::

\endgroup


# Professional Development Coursework

\cvline{2019}{Applied Machine Learning, Max Kuhn, Rstudio::conf workshop.}
\cvline{2018}{Teach the Tidyverse, Garrett Grolemund, Rstudio::conf workshop.}
\cvline{2017}{Advanced Shiny, Joe Cheng, Rstudio::conf workshop.}
\cvline{2015}{Targeted Learning, Sherri Rose, Atlantic Causal Inference Conference short course.}
\cvline{2014}{Applied Predictive Modeling in R, Max Kuhn, useR! Pre-Conference workshop.}
\cvline{2013}{Using Spatial Data, Roger Bivand, useR! Pre-Conference workshop.}
\cvline{2012}{Statistical Modeling in the R Context, Bill Venables, useR! Pre-Conference workshop.}
\cvline{2012}{Geospatial Data in R and Beyond, Barry Rowlingson, useR! Pre-conference workshop.}
\cvline{2012}{Building R Web Applications with Rook, Jeffry Horner, useR! Pre-conference workshop.}
\cvline{2012}{Using the School Attendance Boundary Information System (SABINS), Salvatore Saporito and David Van Riper, AERA Mini-Course.}
\cvline{2011}{R Development Master Class, Hadley Wickham}
\cvline{2011}{Fitting and Evaluating Mixed Models using \texttt{lme4}, Douglas Bates.}
\cvline{2011}{National Assessment of Educational Progress (NAEP) Database training,	National Center for Educational Statistics.}
\cvline{2011}{Presenting Data and Information,	Edward Tufte.}
\cvline{2010}{Handling missing data in R with MICE, Karin Groothuis-Oudshoorn and Stef van Buuren, useR!}
\cvline{2010}{Elastic-R, a google docs-like portal for data analysis in the cloud, Karim Chine, useR!}
\cvline{2009}{Using IPEDS Data for Institutional Effectiveness, Mary Ann Coughlin, NEAIR Workshop.}
\cvline{2009}{Accessing and Analyzing National Databases in Secondary and Higher Education, Terrell L. Strayhorn, AERA Extended Course.}
\cvline{2009}{An Introduction to Hierarchical Linear Modeling with R, J. Kyle Roberts, AERA Mini-Course.}
\cvline{2008}{An Introduction to Propensity Score Analysis, Robert M. Pruzek, University at Albany.}
\cvline{2008}{An Introduction to GIS for Educational Researchers, Mark Hogrebe, Courtney A. Bell, \& Charisse A. Gulosino, AERA Mini-Course.}
\cvline{2008}{Foregrounding Issues of Equity and Diversity in Mathematics Education Research: Implications for Research Methods and Teacher Development, Ban Battey, et al., AERA Mini-Course.}
\cvline{2008}{A ``Gentle" Introduction to Statistical Analysis and Teaching with R, Brandon K. Vaughn, AERA Mini-Course.}

# Graduate Coursework

\cvline{}{\textbf{Completed at the University at Albany}}
\cvline{EPSY 522}{Adolescent Development}
\cvline{EPSY 530}{Statistical Methods I}
\cvline{EPSY 540}{Assessment in Education}
\cvline{EPSY 610}{Advanced Educational Psychology: Learning \& Instruction}
\cvline{EPSY 623}{Advanced Developmental Psychology}
\cvline{EPSY 630}{Statistical Methods II}
\cvline{EPSY 640}{Educational \& Psychological Measurement}
\cvline{EPSY 687}{Institute in Education: Item Response Theory}
\cvline{EPSY 713}{Self-Regulated Learning}
\cvline{EPSY 721}{Comparative Theories in Human Development}
\cvline{EPSY 725}{Seminar in Human Development: Language Development}
\cvline{ECPY 725}{Multivariate Applications in Counseling Psychology}
\cvline{ECPY 726}{Analysis of Covariance Structures}
\cvline{EPSY 735}{Seminar in Statistics (PSA, bootstrapping, factor analysis)}
\cvline{EPSY 761}{History \& Issues in Special Education}
\cvline{EAPS 762}{Seminar in Advanced Research Methods for Educational Leadership (HLM)}
\cvline{EPSY 780}{Seminar in the Profession of Educational Psychology}
\cvline{ETAP 850}{Equity, Diversity, \& Social Justice in Mathematics \& Science Education}
\cvline{EPSY 887}{Institute in Education: The Use of R in Educational Psychology}
\cvline{EPSY 887}{Institute in Education: Modern Graphics for Social Science Research}
\cvline{}{\textbf{Completed at the College of Saint Rose}}
\cvline{EDU 506}{Educational Foundations}
\cvline{EDU 530}{Middle School Education: Theory \& Practice}
\cvline{EDU 590}{Research Seminar}
\cvline{EPY 500}{Educational Research}
\cvline{EPY 502}{Survey of Educational Psychology}
\cvline{SEC 515}{Curriculum \& Instruction in Secondary Schools}
\cvline{SEC 518}{Literacy Improvement in Secondary Schools}
\cvline{SEC 522}{Methods of Teaching Math in Secondary Schools}

\clearpage

# References

\subsection{\textbf{Bruce Dudek, Ph.D.}}
\cvline{}{Professor, Department of Psychology}
\cvline{Email}{\href{mailto:bruce.dudek@albany.edu}{bruce.dudek@albany.edu}}
\cvline{Phone}{(518) 442-4824}
\cvline{Address}{Social Sciences 327\newline University at Albany\newline 1400 Western Ave\newline Albany, NY 12222}

\subsection{\textbf{Lisa Daniels, Ph.D.}}
\cvline{}{Assistant Vice President}
\cvline{Email}{\href{mailto:ldaniels@excelsior.edu}{ldaniels@excelsior.edu}}
\cvline{Phone}{(518) 608-8398}
\cvline{Address}{7 Columbia Circle\newline Albany, NY 12203-5159}

\subsection{\textbf{Heidi Andrade, Ed.D.}}
\cvline{}{Director \& Associate Professor, Division of Educational Psychology \& Methodology}
\cvline{Email}{\href{mailto:handrade@albany.edu}{handrade@albany.edu}}\cvline{Phone}{(518) 437-4422}\cvline{Address}{ED 210, School of Education\newline University at Albany\newline 1400 Western Ave\newline Albany, NY 12222}

