%% start of file `template.tex'.
%% Copyright 2006-2011 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,letterpaper]{moderncv}

%moderncv themes
\moderncvtheme[blue]{classic} % optional argument are 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)


\usepackage[utf8]{inputenc} %character encoding
%\usepackage{hyperref}
%\usepackage{natbib}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates
%\setlength{\maketitlenamewidth}{12cm}       % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details

% personal data
\firstname{Jason M.}
\familyname{Bryer, Ph.D.}
%\title{Senior Research Analyst}
\address{58 Ramsey Place}{Albany, NY 12208}
\mobile{(518) 464-8594}
%\phone{}
%\fax{fax (optional)}
\email{jason@bryer.org}
\homepage{www.bryer.org}
\extrainfo{\href{http://cv.bryer.org}{cv.bryer.org}}
%\photo[64pt][0.4pt]{picture}                  % '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with mutiple entries
\usepackage{multibib}
%\newcites{unpublished}{Unpublished Papers in Preparation}
\newcites{publications}{Published or Submitted}
\newcites{presentations}{Presentations}
\newcites{software}{Software}

\usepackage{natbib}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\vspace{-1.5em} % Added to get more to fit on the first page.

\section{Professional Interests}
\cvline{}{Teaching and research within K-12 and higher education. Specific areas of interest include the use of technology (e.g. R and LaTeX) for reproducible research; academic self-regulated learning; formative assessment; issues of social justice and equity in education; and methodological and statistical topics, particularly propensity score analysis and modern graphics.}

\section{Education}
\cventry{2014}{Ph.D.}{University at Albany}{Albany, NY}{}{Educational Psychology \& Methodology}
\cventry{2009}{M.S.}{University at Albany}{Albany, NY}{}{Educational Psychology \& Methodology}
\cventry{2004-2005}{Coursework Completed}{The College of Saint Rose Graduate School}{Albany, NY}{}{Adolescent Education in Mathematics}
\cventry{1999}{B.A.}{The College of Saint Rose}{Albany, NY}{}{Mathematics major; Computer Information Systems minor}

\section{Dissertation}
\cvline{Title}{\textit{A National Study Comparing Charter and Traditional Public Schools Using Propensity Score Analysis}}
\cvline{Committee}{Robert M. Pruzek (chair), Bruce Dudek (co-chair), Heidi Andrade, Kathryn S. Schiller}
\cvline{Website}{\url{https://github.com/jbryer/Dissertation}}

\section{Professional Experiences}

\cventry{2016-present}{Executive Director \& Principal Investigator}{Excelsior College}{Albany, NY}{}{%
Manage FIPSE First in the World grant to develop a Diagnostic Assessment and Achievement of College Skills (DAACS; \$2,999,877). DAACS provides incoming students with realtime, actionable feedback about their strengths and weaknesses in critical college skills including self-regulation, math, reading, and writing. Additionally, DAACS provides critical information for predictive analytics at the college.\\
Website: \url{http://www.DAACS.net}
}

\cventry{2015-present}{Adjunct Associate Professor}{CUNY School of Professional Studies}{New York, NY}{}{%
Courses taught: IS 606 Statistics \& Probability for Data Analytics (Summer 2015, Fall 2015, Spring 2016, Fall 2016)}

\cventry{2015-present}{Consultant / Learning Analyst}{NYS PBIS Technical Assistance Center}{Albany, NY}{}{%
Developed a data system to support Behavior Specialists work with schools within New York State on their implementation of Positive Behavior Interventions and Supports (PBIS). The goal of this website is to consolidate disparate data sources along with custom data entry so that Behavior Specialists can make data based decisions. I also provided statistical support for analyzing the data at the state level.
Website: \url{http://pbisny.org}
}

\cventry{2014-2015}{Director of Research \& Project Evaluation}{Excelsior College}{Albany, NY}{}{%
Assisted the College in seeking external grants and provide research support for existing grants. Significant activities included:
\begin{itemize}
\item \textbf{Principal Investigator} for a Gates Foundation funded grant (\$168,572) on the use of adaptive learning technology in Biology and Mathematics.
\item \textbf{Lead Evaluator} for New York State Higher Education Services Corporation (HESC) grant (\$449,438) for the expansion of the Online Writing Lab to NYS Community Colleges.
%\item \textbf{Research Lead} for Kresge Foundation funded grant (\$639,000) for the development of Excelsior College's Online Writing Lab.
\end{itemize}
}

\cventry{2009-2015}{Adjunct Instructor}{University at Albany, Division of Educational Psychology \& Methodology}{Albany, NY}{}{%
Courses taught: EPSY 420 Child \& Adolescent Development (Fall 2008, Spring 2009), EPSY 530 Statistics I (Fall 2013, Summer 2014, Fall 2014, Summer 2015), EPSY 887 Computational Statistics (Spring 2013), EPSY 887 Data Science Institute (Fall 2014)}

\cventry{2008-2014}{Senior Research Analyst}{Excelsior College, Office of Institutional Research}{Albany, NY}{}{%
Conducted research and data analysis related to the College's mission. This includes developing, administering, and analyzing surveys; analyzing data from the college's student information system; and consulting with individual schools to develop specific measures. I also provided substantial support and training for other Research Analysts within the Office covering topics such as methodology, statistics, and reproducible research. }

\cventry{2008-2010}{Research Assistant}{Head Start University Partnership for Classroom Quality}{Albany, NY}{}{%
Assisted with data collection, entry, maintenance, and analysis to evaluate the effectiveness of behavioral (Positive Behavior Support [PBS]) and literacy interventions using the Response-to-Intervention (RTI) model.
\newline Principal investigators: Kevin P. Quinn \& Frank R. Vellutino}

\cventry{2008-2011}{Webmaster}{University at Albany, School of Education}{Albany, NY}{}{%
Developed and maintained all School of Education websites.}

\cventry{2006-2007}{Graduate Assistant}{Teaching Mathematics for Understanding, University at Albany}{Albany, NY}{}{%
Developed and led planning sessions with K-8 mathematics teachers in urban school districts on social justice topics in the mathematics curriculum. Assisted in other areas of the project including data collection, conference planning, and development of online professional development courses.
\newline Principal Investigators: Abbe Herzig \& Vicky Kouba}

\cventry{2006-2008}{Senior Applications Developer}{Excelsior College}{Albany, NY}{}{
Developed Java applications for distance learning and student management systems.}

\cventry{2004-2006}{Senior Software Engineer}{State University of New York}{Albany, NY}{}{
Developed web based applications in Java and related technologies as part of a state wide financial and human resource systems.}

\cventry{1999-2004}{Software Engineer}{MapInfo}{Troy, NY}{}{
Contributed key features as part of a geographic information system (GIS) server application (MapXtreme Java) including API for reading and writing binary GIS data, framework for web based applications, and data binding.}

\cventry{1997-1999}{Web Developer}{Office of the Attorney General}{Albany, NY}{}{
Software developer and website designer for the New York State Attorney General's Website.
}



\section{Teaching Experiences}
\cvline{2015 to present}{\textbf{DATA 606 Statistics and Probability for Data Analytics} (CUNY School of Professional Studies)\newline \small This course covers basic techniques in probability and statistics that are important in the field of data analytics. Discrete probability models, sampling from infinite and finite populations, statistical distributions, basic Bayesian statistics, and non-parametric statistical techniques for categorical data are covered in this course. Each of these statistical concepts will be applied in a variety of real-world scenarios through the use of case studies and customized data sets. \newline Course website: \url{http://DATA606.net}}
\cvline{2013 to 2015}{\textbf{EPSY 530 Statistics I} (University at Albany)\newline \small Descriptive statistics including measures of central tendency and variability, correlation and regression. Introduction to statistical inference, including sampling distributions, significance tests, confidence intervals, and power of tests of significance.
\newline Course website: \url{https://github.com/jbryer/EPSY530Summer2015}}
\cvline{Fall 2014}{\textbf{EPSY 887 Data Science Institute} (University at Albany)\newline \small Data Science is the intersection of statistics, computer science, and research. This seminar will introduce the key concepts of data science with an emphasis on data science in education. We will cover the important statistical and programming concepts necessary for conducting reproducible research on large datasets. The open source program R will be used throughout the course. No programming experience is required but at least two semesters of graduate statistics is highly recommended.
\newline Course website: \url{https://github.com/jbryer/EPSY887DataScience}}
\cvline{April/May 2014}{\textbf{Applied Propensity Score Analysis with R} (Workshop given at the University at Albany)
\newline \small This two day workshop provided an introduction to propensity score methods using R as well as more advanced topics including multilevel PSA, non-binary treatment matching, and bootstrapping.
\newline Workshop website: \url{http://psa.bryer.org}}
\cvline{Spring 2013}{\textbf{EPSY 887 Institute in Education: Computational Statistics} (University at Albany)\newline \small This seminar will provide an introduction to statistical programming for data analysis with an emphasis on the analysis of large datasets. With the increased availability of large national and international datasets (e.g. PISA, TIMMS, NAEP, ECLS) there is a great opportunity and potential for researchers to address important questions. However, the analysis of large datasets requires special analytical procedures not found in commercial statistics software. Utilizing the open source statistical software R, students will be introduced to the tools and procedures for analyzing large datasets with an emphasis on conducting transparent and reproducible research.
\newline Course website: \url{https://github.com/jbryer/CompStats}}
\cvline{July 2013}{\textbf{Introduction to Propensity Score Methods with R} (useR! 2013 Pre-Conference Workshop)\newline This workshop will provide participants with a theoretical overview of propensity score methods as well as illustrations and discussion of PSA applications using R.}
\cvline{Fall 2016\\Fall 2015\\Fall 2013\\Fall 2012\\Fall 2011}{\textbf{Introduction to R and LaTeX for Institutional Research} (Workshop given at the Northeast Association for Institutional Research)\newline \small This workshop provides an overview as well as hands-on exercises for using R and LaTeX to perform data analysis and report generation. Participants learn to perform basic statistical analyses in R and to generate reports with LaTeX in spreadsheet, presentation, and document formats.}
\cvline{Spring 2009\\Fall 2008}{\textbf{EPSY 420 Child \& Adolescent Development} (University at Albany)\newline \small This course covers theory and research in social, emotional, physical, and intellectual development and its application to instruction with an emphasis on late childhood through middle adolescence.}
\cvline{2007-2012\\Fall Semesters}{Assisted in teaching the online section of Statistics I (EPSY 530) including the installation and management of the Moodle Content Management System ({\href{http://moodle.bryer.org}{moodle.bryer.org}}).}


\section{Service Positions}
\cvline{2014-present}{Founding Organizer of the Albany R Users Group\newline Website: \url{http://www.meetup.com/Albany-R-Users-Group}}
\subsection{Dissertation Committees}
\cvline{current}{Kimberly Speershneider - The Differentiated Impact Of Early Entry Into Head Start On Social Competence And Literacy: An Applied Propensity Score Analysis}
\cvline{2015}{Chrisopher Valle - Effects Of Criteria-Referenced Formative Assessment On Achievement In Music}
\cvline{2015}{Fei Chen - The Impact of Criteria-Referenced Formative Assessment On Fifth Grade Students' Theater Arts
And English Language Arts Achievement}
\subsection{Excelsior College}
\cvline{2015-present}{Chair, Diagnostic Assessment \& Achievement of College Skills Advisory Committee}
\cvline{2014-present}{Chair, Technology Advisory Subcommittee}
\cvline{2014-present}{Committee Member, Information Technology Committee}
\cvline{2013-2014}{Committee Member, Persistence Measure Task Force}
\cvline{2010-2014}{Committee Member, Student Learning Support Services Committee}
\cvline{2010-2014}{Committee Member, Data Definitions \& Quality}
\cvline{2010-2013}{Committee Member, Information Technology Operations \& Security Committee}
\cvline{2011-2012}{Committee Member, Search Committee for Assistant Provost}
\cvline{2009-2010}{Committee Member, Early Alert System for Identifying Non-Persistent Students}
\cvline{2009}{Chair, Task Force on a Library of Model Courses}
\cvline{2009-2010}{Committee Member, System for Storing Information at Excelsior College}
\subsection{City School District of Albany}
\cvline{2011-2012}{\small Committee Member, Grade Configuration Committee; Chair of the Accountability Subcommittee}
\subsection{American Educational Research Association}
\cvline{2009-2011}{Treasurer, Studying and Self-Regulated Learning Special Interest Group}
\cvline{2009-2010}{Committee Member, Division D Membership Committee}
\subsection{University at Albany, Division of Educational Psychology \& Methodology}
\cvline{2007-2008}{Treasurer, Graduate Student Organization}

\renewcommand{\listitemsymbol}{}            % change the symbol for lists

\section{Professional Memberships}
\cvline{AERA}{\href{http://aera.net}{American Educational Research Association}}
\cvline{AIR}{\href{http://www.airweb.org/}{Association for Institutional Research}}
\cvline{ASA}{\href{http://www.amstat.org/}{American Statistical Association}}
%\cvline{MAA}{\href{http://www.maa.org/}{Mathematical Association of America}}
%\cvline{NCTM}{\href{http://www.nctm.org/}{National Council of Teachers of Mathematics}}
\cvline{NEAIR}{\href{http://www.neair.org}{North East Association for Institutional Research}}
\cvline{NCME}{\href{http://www.ncme.org}{National Council on Measurement in Education}}
%\cvline{STP}{\href{http://teachpsych.org/}{Society for the Teaching of Psychology}}

\section{Awards \& Grants}
\cvline{2015-2019}{\textbf{Principal Investigator} \href{http://www.ed.gov/news/press-releases/department-awards-60-million-first-world-grants-17-colleges-universities-and-organizations}{FIPSE First in the World} grant (\$2,999,877, P116F150077), \textit{Diagnostic Assessment \& Achievement of College Skills: Personalized Feedback \& Targeted Student Supports}.}
\cvline{2013-2015}{\textbf{Principal Investigator} Bill \& Melinda Gates Foundation grant (\$168,572) on the use of adaptive learning technology in introductory Biology and Mathematics courses.}
\cvline{2014-2016}{\textbf{Lead Evaluator} for a New York State Higher Education Services Corporation (HESC) grant (\$449,438) for the expansion of the Online Writing Lab to NYS Community Colleges.}
\cvline{2013}{North East Association for Institutional Research (NEAIR) Ambassador Grant (\$800)}
\cvline{2013}{Excelsior College, Employee Recognition Award for Excellence in Innovation}
\cvline{2011, 2012}{The Society of Multivariate Experimental Psychology (SMEP), Workshop Travel Award (three separate awards of \$1,000 each)}
\cvline{2011}{National Center for Educational Statistics Workshop Travel Award (\symbol{126}\$800)}
\cvline{2009}{Association for Institutional Research (AIR) \& National Center for Educational Statistics (NCES), Travel Grant (\$330)}
\cvline{2009}{National Science Foundation, Travel/Research Grant (\$1,000)}
\cvline{2009}{University at Albany Graduate Student Organization, Travel/Research Grant (\$320.00)}
\cvline{2001}{Award for Outstanding Performance, MapInfo.}
\cvline{1999}{Sister Noel Marie Cronin Award for excellence in Mathematics, College of Saint Rose.}
\cvline{1999}{Outstanding Senior Award for Mathematics/Computer Information Systems, College of Saint Rose.}
\cvline{1998, 1999}{Service and Appreciation Award, College of Saint Rose.}

% Publications from a BibTeX file without multibib
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{}}% for BibTeX numerical labels
%\bibliographystyle{plain}
%\bibliography{publications}                  % 'publications' is the name of a BibTeX file
%\nocite{*}

% Publications from a BibTeX file using the multibib package
%Unpublished papers in preparation
% \nociteunpublished{TriMatchJSS,multilevelPSAJSS,PSAbootJSS,likertRJournal}
% \bibliographystyleunpublished{apa-custom}
% \bibliographyunpublished{BryerReferences}
%Published or submitted
\nocitepublications{bryer2018,anderson2013,nursingMeasurement,mbr2011,factbook}
\bibliographystylepublications{apa-custom}
\bibliographypublications{BryerReferences}
%Presentations
\nocitepresentations{nera2017,acic2015,osf2015,aascu2014,user2014PSAboot,user2012TriMatch,user2012likert,user2012,aera2012,ira2012,ualbanysoe2012,neair2011,smep2011a,smep2011b,user2011,air2011,strose2011,edpsychposter2011,edpsych2011,excelsior2011,lra2010,neair2010,ies2010,air2010,edpsychposter2010,neair2009,nera2009a,nera2009b,dsc2009,edpsychposter2009,aera2009,nera2008,ualbany2008,edpsych2007,edpsychposter2007,hrumc1998,hrumc1997}
\bibliographystylepresentations{apa-custom}
\bibliographypresentations{BryerReferences}
%Software
% \clearpage
\nocitesoftware{PSAboot,TriMatch,multilevelPSA,likert,sqlutils,naep,makeR,irutils,ruca,ipeds,qualtrics,irutils,FractalJ}
\bibliographystylesoftware{apa-custom}
\bibliographysoftware{BryerReferences}


\clearpage


\section{Professional Development Coursework}
\cvline{2017}{Advanced Shiny, Joe Cheng, Rstudio::conf workshop.}
\cvline{2015}{Targeted Learning, Sherri Rose, Atlantic Causal Inference Conference short course.}
\cvline{2014}{Applied Predictive Modeling in R, Max Kuhn, useR! Pre-Conference workshop.}
\cvline{2013}{Using Spatial Data, Roger Bivand, useR! Pre-Conference workshop.}
\cvline{2012}{Statistical Modeling in the R Context, Bill Venables, useR! Pre-Conference workshop.}
\cvline{2012}{Geospatial Data in R and Beyond, Barry Rowlingson, useR! Pre-conference workshop.}
\cvline{2012}{Building R Web Applications with Rook, Jeffry Horner, useR! Pre-conference workshop.}
\cvline{2012}{Using the School Attendance Boundary Information System (SABINS), Salvatore Saporito and David Van Riper, AERA Mini-Course.}
\cvline{2011}{R Development Master Class, Hadley Wickham}
\cvline{2011}{Fitting and Evaluating Mixed Models using \texttt{lme4}, Douglas Bates.}
\cvline{2011}{National Assessment of Educational Progress (NAEP) Database training,	National Center for Educational Statistics.}
\cvline{2011}{Presenting Data and Information,	Edward Tufte.}
\cvline{2010}{Handling missing data in R with MICE, Karin Groothuis-Oudshoorn and Stef van Buuren, useR!}
\cvline{2010}{Elastic-R, a google docs-like portal for data analysis in the cloud, Karim Chine, useR!}
\cvline{2009}{Using IPEDS Data for Institutional Effectiveness, Mary Ann Coughlin, NEAIR Workshop.}
\cvline{2009}{Accessing and Analyzing National Databases in Secondary and Higher Education, Terrell L. Strayhorn, AERA Extended Course.}
\cvline{2009}{An Introduction to Hierarchical Linear Modeling with R, J. Kyle Roberts, AERA Mini-Course.}
\cvline{2008}{An Introduction to Propensity Score Analysis, Robert M. Pruzek, University at Albany.}
\cvline{2008}{An Introduction to GIS for Educational Researchers, Mark Hogrebe, Courtney A. Bell, \& Charisse A. Gulosino, AERA Mini-Course.}
\cvline{2008}{Foregrounding Issues of Equity and Diversity in Mathematics Education Research: Implications for Research Methods and Teacher Development, Ban Battey, et al., AERA Mini-Course.}
\cvline{2008}{A ``Gentle" Introduction to Statistical Analysis and Teaching with R, Brandon K. Vaughn, AERA Mini-Course.}

\clearpage
\section{Graduate Coursework}
\cvline{}{\textbf{Completed at the University at Albany}}
\cvline{EPSY 522}{Adolescent Development}
\cvline{EPSY 530}{Statistical Methods I}
\cvline{EPSY 540}{Assessment in Education}
\cvline{EPSY 610}{Advanced Educational Psychology: Learning \& Instruction}
\cvline{EPSY 623}{Advanced Developmental Psychology}
\cvline{EPSY 630}{Statistical Methods II}
\cvline{EPSY 640}{Educational \& Psychological Measurement}
\cvline{EPSY 687}{Institute in Education: Item Response Theory}
\cvline{EPSY 713}{Self-Regulated Learning}
\cvline{EPSY 721}{Comparative Theories in Human Development}
\cvline{EPSY 725}{Seminar in Human Development: Language Development}
\cvline{ECPY 725}{Multivariate Applications in Counseling Psychology}
\cvline{ECPY 726}{Analysis of Covariance Structures}
\cvline{EPSY 735}{Seminar in Statistics (PSA, bootstrapping, factor analysis)}
\cvline{EPSY 761}{History \& Issues in Special Education}
\cvline{EAPS 762}{Seminar in Advanced Research Methods for Educational Leadership (HLM)}
\cvline{EPSY 780}{Seminar in the Profession of Educational Psychology}
\cvline{ETAP 850}{Equity, Diversity, \& Social Justice in Mathematics \& Science Education}
\cvline{EPSY 887}{Institute in Education: The Use of R in Educational Psychology}
\cvline{EPSY 887}{Institute in Education: Modern Graphics for Social Science Research}
\cvline{}{\textbf{Completed at the College of Saint Rose}}
\cvline{EDU 506}{Educational Foundations}
\cvline{EDU 530}{Middle School Education: Theory \& Practice}
\cvline{EDU 590}{Research Seminar}
\cvline{EPY 500}{Educational Research}
\cvline{EPY 502}{Survey of Educational Psychology}
\cvline{SEC 515}{Curriculum \& Instruction in Secondary Schools}
\cvline{SEC 518}{Literacy Improvement in Secondary Schools}
\cvline{SEC 522}{Methods of Teaching Math in Secondary Schools}

\clearpage
\section{References}

%\subsection{Robert Pruzek, Ph.D.}
%\cvline{}{Professor, Division of Educational Psychology \& Methodology}
%\cvline{Email}{\href{mailto:rmpruzek@albany.edu}{rmpruzek@albany.edu}}
%\cvline{Phone}{(518) 793-4395}
%\cvline{Address}{ED 225, School of Education\newline University at Albany\newline 1400 Western Ave\newline Albany, NY 12222}

\subsection{Bruce Dudek, Ph.D.}
\cvline{}{Professor, Department of Psychology}
\cvline{Email}{\href{mailto:bruce.dudek@albany.edu}{bruce.dudek@albany.edu}}
\cvline{Phone}{(518) 442-4824}
\cvline{Address}{Social Sciences 327\newline University at Albany\newline 1400 Western Ave\newline Albany, NY 12222}

\subsection{Lisa Daniels, Ph.D.}
\cvline{}{Assistant Vice President}
\cvline{Email}{\href{mailto:ldaniels@excelsior.edu}{ldaniels@excelsior.edu}}
\cvline{Phone}{(518) 608-8398}
\cvline{Address}{7 Columbia Circle\newline Albany, NY 12203-5159}

\subsection{Heidi Andrade, Ed.D.}
\cvline{}{Associate Dean for Academic Affairs, School of Education}
\cvline{}{Associate Professor, Division of Educational Psychology \& Methodology}
\cvline{Email}{\href{mailto:handrade@albany.edu}{handrade@albany.edu}}\cvline{Phone}{(518) 437-4422}\cvline{Address}{ED 210, School of Education\newline University at Albany\newline 1400 Western Ave\newline Albany, NY 12222}

%\subsection{Patrick Jones, Ph.D.}
%\cvline{}{Vice Provost, Excelsior College}
%\cvline{Email}{\href{mailto:pjones@excelsior.edu}{pjones@excelsior.edu}}
%\cvline{Phone}{(518) 464-8778}
%\cvline{Address}{7 Columbia Circle\newline Albany, NY 12203-5159}

\subsection{Joan Newman, Ph.D.}\cvline{}{Director \& Associate Professor, Division of Educational Psychology \& Methodology}
\cvline{Email}{\href{mailto:joanewman@gmail.com}{joanewman@gmail.com}}\cvline{Phone}{(518) 442-4781}\cvline{Address}{ED 236, School of Education\newline University at Albany\newline 1400 Western Ave\newline Albany, NY 12222}

\end{document}


%% end of file `template_en.tex'.
