ignoreFiles = ["\\.Rmd$", "\\.Rmarkdown$", "_files$", "_cache$", "\\.xlsx$"]
publishDir = "../docs/"
baseURL = "/"
languageCode = "en"
title = ""
theme = "hugo-devresume-theme"
googleAnalytics = "UA-XXXXXXX-Y"

```{r setup, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
library(readxl)
library(bib2df)

experiences <- readxl::read_excel('data/Experience.xlsx')
education <- readxl::read_excel('data/Education.xlsx')
awards <- readxl::read_excel('data/Awards.xlsx')
projects <- readxl::read_excel('data/Projects.xlsx')
publications <- bib2df::bib2df('bib/Published.bib')

bio <- markdown::markdownToHTML('bio.md', fragment.only = TRUE)
bio <- gsub('\n', '', bio)
bio <- gsub('"', "'", bio)
```

[params]
    author = "Jason Bryer, Ph.D."
    description = ""

    primaryColor = "#2E86C1"
    textPrimaryColor = "#292929"

    [params.profile]
        enable = true
        name = "Jason Bryer, Ph.D."
        tagline = "Academic Researcher and Teacher"
        avatar = "Headshot_Cartoon.jpg"


    [params.summary]
        enable = true
        text = "`r bio`"


    [params.contact]
        enable = true
        location = "Albany, New York"

        [[params.contact.list]]
        icon = "fas fa-phone-square"
        url = "tel:#"
        text = "518-464-8594"
        [[params.contact.list]]
        icon = "fas fa-envelope-square"
        url = "mailto:#"
        text = "jason@bryer.org"
        [[params.contact.list]]
        icon = "fas fa-globe"
        url = "#"
        text = "www.bryer.org"
        [[params.contact.list]]
        icon = "fas fa-file-pdf"
        url = "https://github.com/jbryer/CV/blob/master/Bryer_CV.pdf?raw=true"
        text = "Download CV"

    [params.skills]
        enable = false

        [[params.skills.list]]
        title = "Teaching and research within K-12 and higher education"
        [[params.skills.list.items]]
        details = "JavaScript/Angular/React/Vue"
        [[params.skills.list.items]]
        details = "Python/Ruby/PHP"
        [[params.skills.list.items]]
        details = "Node.js/ASP.NET"
        [[params.skills.list.items]]
        details = "PostgreSQL/MySQL"
        [[params.skills.list.items]]
        details = "Object-oriented design"
        [[params.skills.list.items]]
        details = "Design and implement database structures"
        [[params.skills.list.items]]
        details = "Lead and deliver complex software systems"

        [[params.skills.list]]
        title = "Professional"
        [[params.skills.list.items]]
        details = "Effective communication"
        [[params.skills.list.items]]
        details = "Team player"
        [[params.skills.list.items]]
        details = "Strong problem solver"
        [[params.skills.list.items]]
        details = "Good time management"

    [params.education]
        enable = true

```{r education, results = 'asis'}
for(i in 1:nrow(education)) {
    cat("        [[params.education.list]]\n", sep = '')
    cat("        degree = \"", education[i,]$Degree, "\"\n", sep = '')
    cat("        university = \"", education[i,]$Institution, "\"\n", sep = '')
    cat("        dates = \"", education[i,]$Year, "\"\n", sep = '')
}
```

    [params.awards]
        enable = false

```{r awards, results = 'asis'}
for(i in 1:nrow(awards)) {
	cat("        [[params.awards.list]]\n", sep = '')
	cat("        name = \"", awards[i,]$Title, ' ', awards[i,]$Description, "\"\n", sep = '')
	cat("        year = \"", awards[i,]$Year, "\"\n", sep = '')
}
```

    [params.languages]
        enable = true

        [[params.languages.list]]
        name = "English"
        level = "Native"
        [[params.languages.list]]
        name = "R"
        level = "Professional"


    [params.interests]
        enable = true

        [[params.interests.list]]
        name = "Teaching and research within K-12 and higher education"
        [[params.interests.list]]
        name = "Data Science"
        [[params.interests.list]]
        name = "Reproducible Research"
        [[params.interests.list]]
        name = "Statistics"
        [[params.interests.list]]
        name = "Causal Inference"
        [[params.interests.list]]
        name = "Propensity Score Analysis"
        [[params.interests.list]]
        name = "R"
        [[params.interests.list]]
        name = "Data Visualization"
        [[params.interests.list]]
        name = "Self-Regulated Learning"
        [[params.interests.list]]
        name = "College Readiness"


    [params.experience]
        enable = true

```{r experiences, results='asis'}
for(i in seq_len(nrow(experiences))) {
	cat('        [[params.experience.list]]\n', sep = '')
	cat('        title = "', experiences[i,]$Title, '"\n', sep = '')
	cat('        dates = "', experiences[i,]$Start, ' to ', experiences[i,]$End, '"\n', sep = '')
	cat('        company = "', experiences[i,]$Institution, '"\n', sep = '')
	cat('        details = "',gsub('[\n\r]', '<br/>', experiences[i,]$Description), '"\n\n', sep = '')
}
```


    [params.projects]
        enable = true

```{r projects, results='asis'}
for(i in seq_len(nrow(projects))) {
	cat('       [[params.projects.list]]\n', sep = '')
	cat('        title = "', projects[i,]$Title, '"\n', sep = '')
	cat('        link = "', projects[i,]$URL, '"\n', sep = '')
	cat('        meta = "', projects[i,]$Meta, '"\n', sep = '')
	cat('        tagline = "', projects[i,]$Description, '"\n\n', sep = '')
}
```


    [params.information]
        enable = true

        [[params.information.list]]
        title = "Publications"
```{r publications, results='asis'}
for(i in seq_len(nrow(publications))) {
	cat('        [[params.information.list.items]]\n', sep = '')
	cat('        details = "(', publications[i,]$YEAR, ') ', publications[i,]$TITLE, '"\n', sep = '')
}
```

        [[params.information.list]]
        title = "Interests"
        details = "Running, Photography, Guitar"


    [params.social]
        enable = true

        [[params.social.list]]
        icon = "fab fa-github-square"
        url = "//github.com/jbryer"
        title = "jbryer"
        [[params.social.list]]
        icon = "fab fa-linkedin"
        url = "//linkedin.com/in/jasonbryer"
        title = "jasonbryer"
        [[params.social.list]]
        icon = "fab fa-twitter-square"
        url = "//twitter.com/jbryer"
        title = "@jbryer"

